Summer 2025 ToDo

### 2025-06-18 Relations/Paper/Formalization.tex
Rewording the intro to base.agda

Most standard termination and confluence properties are defined in the file \texttt{Properties.agda} and related files discussed in the previous section.  The file \texttt{Base.agda} imports all of these files
and introduces a few more notations used specifically for formalizing chapter 1 of \cite{Terese}.
\apcomment{Discuss these...}

The closure operators are formalized in \texttt{ClosureOperators.agda}.
The definitions grouped as confluent in \terese $\,$ are formalized in \texttt{Base.agda}.
The definitions grouped as normalizing in \terese $\,$ are formalized in \texttt{Properties.agda}.

>>>>

As outlined in the previous section, \texttt{Properties.agda}, \texttt{Seq.agda}, and \texttt{ClosureOperators.agda} define most standard termination and confluence properties. The file \texttt{Base.agda} introduces additional defitions which are required for the formalization of the propositions found in Chapter 1 of \terese.
